---
title: "TravellingSalesman Heli Layout"
author: "Kiri Daust"
date: "14/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(clhs)
library(sf)
library(raster)
library(sp)
library(gdistance)
library(foreach)
library(data.table)
library(fasterize)
library(reticulate)
library(here)
```

## Intro

This script uses cost constrained latin hypercube and a travelling salesman algorithm to create a sample plan for helicopter work in the ESSF of the Deception AOI. 

### Source scripts

```{r source}
Rcpp::sourceCpp("CppCLHS.cpp")
source("FastCLHS_R.R")
source_python("./mTSP.py")
```

### Load data

Set aoi to ESSFmc or ESSFmcw depending on interest.

```{r data}
aoi <- "ESSFmc"
datLocGit <- here("InputData") ## Data
covLoc <- here("Covariates") ## Too big for git data
### landscape levels covariates
covars <- paste(covLoc, c("25m_DAH_3Class.tif","25m_LandformClass_Default_Seive4.tif",
                          "25m_MRVBF_Classified_IS64Low6Up2.tif","dem.tif"), sep = "/")# ,"DEM_25m.tif"
layerNames <- c("DAH","LFC","MRVBF","DEM","cost") ##need to change this if you change the layers
ancDat <- raster::stack(covars)
proj4string(ancDat) <- "+init=epsg:3005"

# read in slope data
slope_raster <-  grep("^slope", list.files(covLoc))
slope <- raster(list.files(covLoc, full.name = TRUE)[slope_raster])
proj4string(slope) <- "+init=epsg:3005"

## dem for transtion layer
alt <- raster(paste0(covLoc, "/dem.tif"))
proj4string(alt) <- "+init=epsg:3005"

##road and lake buffer
buff <- st_read(paste0(datLocGit,"/ESSF_Buffer.gpkg"))

## clip to just ESSF
boundary <- st_read(paste0(datLocGit,"/bec_edited.gpkg"))
boundary <- boundary[,"MAP_LABEL"]
boundary <- boundary[boundary$MAP_LABEL == aoi,] ## set as mask for individual BGC
b2 <- st_union(boundary)
b2 <- fasterize(boundary, slope)
buff <- fasterize(buff, slope)
buff <- mask(buff,b2)
ancDat <- mask(ancDat,buff)

##read in drop points
heliDrop <- st_read(paste0(datLocGit,"/DropCombined.gpkg"))
heliDrop <- heliDrop[,"name"]
heliDrop <- st_transform(heliDrop, 3005)
heliDrop <- st_zm(heliDrop)
heliDrop <- heliDrop[boundary,]
start <- as(heliDrop, "Spatial")

# read in already sampled locations
included <- st_read(paste0(datLocGit,"/ESSF_sampledpairs.gpkg"))
included <- st_transform(included, st_crs(ancDat))
included <- included[boundary,]
#if(nrow(included) == 0){included = NULL}
```

### Create transition layer

This chunk creates a transition layer from the DEM to account for downhill and uphill sections. It uses an adaptions to Tobler's hiking function to calculate potential walking speed. 

```{r translayer}
altDiff <- function(x){x[1]-x[2]}
tr <- transition(alt, transitionFunction = altDiff, directions = 8, symm = F) 
tr <- geoCorrection(tr)
adj <- adjacent(alt, cells = 1:ncell(alt), pairs = T, directions = 8)
tr[adj] <- 1.5*exp(-3.5*abs(tr[adj] + 0.1)) ##tobler's hiking function

tr <- geoCorrection(tr)
```

### Setup to run TSP

```{r setup}
##max time per day
maxTime <- 8L ##hours
## time per transect
plotTime <- 45L ##mins

listComb <- function(a,b){
  t1 <- rbind(a$sampled_data,b$sampled_data)
  t2 <- b$obj
  t3 <- c(a$final_obj,b$final_obj)
  list(sampled_data = t1, obj = t2, final_obj = t3)
}

###main function to create layout
createLayout <- function(startPnts, toInclude, nPoints, iter = 1000){
  isInc <- nrow(toInclude) > 0
  spoints <- foreach(x = 1:2, .combine = listComb) %do% {##run one slice per drop point
    acost <- accCost(tr, startPnts[x,])
    acost <- acost/3600
    lays <- stack(ancDat,acost)
    names(lays) <- layerNames
    
    if(isInc){
      incPnts <- raster::extract(lays, toInclude, sp = T)
      incPnts <- incPnts[,-(1:3)]
      incPnts <- st_as_sf(incPnts)
      incIdx <- 1:nrow(incPnts)
      size = nPoints/2 + nrow(incPnts)
    }else{
      incIdx <- NULL
      size = nPoints/2
    }
    
    if(x == 2){ ##add points from slice 1
      inc2 <- templhs$sampled_data
      temp <- raster::extract(acost, inc2["geometry"], sp = T) %>% st_as_sf()
      inc2$cost <- temp$layer
      if(isInc) incPnts <- rbind(incPnts, inc2)
      else incPnts <- inc2
      incIdx <- 1:nrow(incPnts)
      size = nPoints/2 + nrow(incPnts)
    }
    
    s <- sampleRegular(lays , size = 5000000, sp = TRUE) # sample raster
    s <- s[!is.na(s$DAH) & !is.infinite(s$cost),]
    s <- st_as_sf(s)
    ## have to add already sampled points to data
    if(isInc | x == 2 ) s <- rbind(incPnts, s)
    
    ### run clhs (new parameters are minDist and maxCost)
    templhs <- clhs_dist(s,size = size, minDist = 260, 
                         maxCost = 2, include = incIdx, 
                         cost = "cost", iter = iter, simple = F,progress = T)
    
    list(sampled_data = templhs$sampled_data,obj = templhs$obj, final_obj = templhs$final_obj)
  }

  pnts <- spoints$sampled_data
  
  plot(acost)
  plot(pnts, add = T)
  
  p2 <- st_as_sf(pnts)
  pnts <- pnts[,"DAH"]
  colnames(pnts) <- c("name","geometry")
  st_geometry(pnts) <- "geometry"
  startPnts <- st_as_sf(startPnts) %>% st_transform(st_crs(pnts))
  pnts <- rbind(pnts, startPnts)
  pnts2 <- as(pnts, "Spatial")
  
  ## create distance matrix between sample points
  test <- costDistance(tr,pnts2,pnts2)
  dMat2 <- as.matrix(test)
  dMat2 <- dMat2/60
  dMat2[is.infinite(dMat2)] <- 1000
  
  ##penalty based on quality of points
  objVals <- spoints[["final_obj"]][1:nPoints]
  objVals <- max(objVals) - objVals
  minPen <- (maxTime*60L)/2L
  maxPen <- (maxTime*60L)*2L
  objVals <- scales::rescale(objVals, to = c(minPen,maxPen))
  objVals <- as.integer(objVals)

  ##fixed start, arbitrary end
  dMat2 <- rbind(dMat2, rep(0, ncol(dMat2)))
  dMat2 <- cbind(dMat2, rep(0, nrow(dMat2)))
  indStart <- as.integer(nPoints:(nPoints+nrow(startPnts)-1))
  indEnd <- as.integer(rep(nrow(dMat2)-1,nrow(startPnts)))
  
  ##run vehicle routing problem from python script
  ## GCS is global span cost coefficient
  vrp <- py_mTSP(dat = dMat2,num_days = 2L, start = indStart, end = indEnd, 
                 max_cost = maxTime*60L, plot_time = plotTime, penalty =  objVals, arbDepot = T, GSC = 8L)
  
  return(list(route = vrp, objective = spoints$obj[iter],pnts = pnts))
}

```

### Set up parallel workers

```{r parallel}
worker.init <- function(){
  Rcpp::sourceCpp("CppCLHS.cpp")
}

require(doParallel)
cl <- makePSOCKcluster(detectCores()-2)
clusterCall(cl, worker.init)
registerDoParallel(cl)
```

### Create layout for each combination of dropsites

```{r runLayout}
dropInd <- 1:nrow(heliDrop)
combs <- combn(dropInd, m = 2) ## pair combinations

### run clhs and tsp
outStats <- foreach(i = 1:ncol(combs), .combine = c, 
                    .packages = c("Rcpp","reticulate","sf","raster","gdistance","foreach"),
                    .noexport = "c_cor") %dopar% {
  source_python("./mTSP.py")
  res <- createLayout(startPnts = start[c(combs[1,i],combs[2,i]),],toInclude = included, nPoints = 10)
  route <- res$route
  temp <- data.frame(start = paste(combs[1,i],combs[2,i],sep = "_"),cost = sum(unlist(route[[2]])), 
             num = paste(length(route[[1]][["0"]]),length(route[[1]][["1"]])), objFun = res$objective,
             totNum = sum(length(route[[1]][["0"]]),length(route[[1]][["1"]])))
  out <- list(list(stats = temp, solution = route,points = res$pnts))
  names(out) <- i
  out
}

### extract statistics from result
stats <- foreach(i = 1:ncol(combs), .combine = rbind) %do% {
  outStats[[i]][["stats"]]
}
##subset to runs with 5 transects in each drop
stats <- stats[stats$num == "6 6",]
ids <- rownames(stats[order(stats$cost),])
```

### Create shortest paths and output routes

```{r output}

## function to create and output layout for each id
writeLayout <- function(id,filename){
  vrp <- outStats[[id]][["solution"]]
  pnts <- outStats[[id]][["points"]]
  result <- vrp[[1]]
  
  ## create spatial paths
  paths <- foreach(j = 0:(length(result)-1), .combine = rbind) %do% {
    if(length(result[[as.character(j)]]) > 2){
      cat("Drop site",j,"...\n")
      p1 <- result[[as.character(j)]]+1
      out <- foreach(i = 1:(length(p1)-1), .combine = rbind) %do% {
        temp1 <- pnts[p1[i],]
        temp2 <- pnts[p1[i+1],]
        temp3 <- shortestPath(tr,st_coordinates(temp1),
                              st_coordinates(temp2),output = "SpatialLines") %>% st_as_sf()
        temp3$Segment = i
        temp3
      }
      out$DropSite = j
      out
    }
    
  }

  paths <- st_transform(paths, 3005)
  st_write(paths, dsn = filename, layer = "Paths", append = T, driver = "GPKG")  
  
  ## label points
  p2 <- pnts
  p2$PID <- seq_along(p2$name)
  p2 <- p2[,"PID"]
  p2$DropLoc <- NA
  p2$Order <- NA
  for(i in 0:(length(result)-1)){
    p1 <- result[[as.character(i)]]+1
    p1 <- p1[-1]
    p2$DropLoc[p1] <- i
    p2$Order[p1] <- 1:length(p1)
  }
  p2 <- st_transform(p2, 3005)
  st_write(p2, dsn = filename,layer = "Points", append = T,overwrite = T, driver = "GPKG")
  return(TRUE)
}

## write gpkgs for each full route
for(x in 1:length(ids)){
  writeLayout(id = ids[x], filename = paste0("ESSFmc_",x,".gpkg"))
}
```
